---
title: "University of Sri Jayewardenepura, Sri Lanka"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
    logo: logo/unilogo.png
runtime: shiny
css: styles.css
---

<style>                     
.navbar {
  background-color:#800000;
  border-color:#800000;
  font-weight: 900;
}
.navbar-brand {
color:#fed976!important;
}

.navbar-logo img {
    position: absolute;
    right: 0px;
    width: 50px;
    height: 50px;
    border-radius: 70%;
    overflow: hidden;
    margin-top: 2px;
}

</style> 

```{r setup, include=FALSE}
library(flexdashboard)
library(patchwork)
library(stringr)
library(knitr)
library(viridis)
library(viridisLite)
```

# Internal Undergraduates 

Column {data-width=300}
-----------------------------------------------------------------------


```{r, echo=FALSE, warning=FALSE, message=FALSE}
library(tidyverse)
library(plotly)
order1 <- c("Management Studies & Commerce", "Humanities & Social Sciences", "Applied Sciences", "Technology", "Medical Sciences", "Engineering", "Allied Health Sciences")
faculty_names <- factor(c("Humanities & Social Sciences", "Applied Sciences", "Management Studies & Commerce", "Medical Sciences", "Technology", "Engineering", "Allied Health Sciences"), levels=rev(order1))


new_registrations <- c(984, 875, 1348, 193, 491, 186, 155)
total_registration <- c(3568, 2678, 4966, 1177, 1438,540, 395)
df1 <- tibble(faculty_names,
              new_registrations,
                  total_registration)
df12 <- pivot_longer(df1, 2:3, "Type", "Count") 
#p1 <- ggplot(df12, aes(y=value, x=reorder(faculty_names, value), fill=Type)) + geom_bar(stat="identity") +  scale_fill_manual(values = c("#1b9e77","#d95f02")) + labs(x="", y="Number of students") + theme(legend.position="bottom", axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
#ggplotly(p1)



```



### Figure 1.1: Total number of registered by year (as at 31 December 2021)


```{r, fig.height=10}
# Internal undergraduate enrolment (Total number of registered) as at 31st December (2017-2021)
vec1p <- c("#0D0887FF", "#6A00A8FF", "#B12A90FF", "#E16462FF", "#FCA636FF", "#F0F921FF")
vec2g <- c("#FDE725FF", "#7AD151FF", "#22A884FF", "#2A788EFF", "#414487FF", "#440154FF")
vec3 <- c("#fed976", "#feb24c", "#fd8d3c", "#f03b20", "#bd0026")
vec4 <- c("#253494", "#2c7fb8", "#41b6c4", "#7fcdbb", "#c7e9b4")
y2017 <- c(3296, 2021, 4804, 804, 642, 241, 333)
y2018 <- c(3341, 2251, 4794, 938, 642, 362, 280)
y2019 <- c(3458, 2222, 4659, 948, 947, 458, 290)
y2020 <- c(3462, 2464, 4843, 948, 947, 458, 290)
y2021 <- c(3568, 2678, 4966, 1177, 1438, 540, 395)
df2 <- tibble(faculty_names, y2017, y2018, y2019, y2020, y2021)
colnames(df2) <- c("Faculty", "2017", "2018", "2019", "2020", "2021")
df21 <- pivot_longer(df2, 2:6, "Year", "Value")
p2 <- ggplot(df21, aes(x=Faculty, y=value,  fill=Year)) + geom_bar(stat="identity", position="dodge") +  scale_fill_manual(values=rev(vec2g))+theme( axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) + labs(x="", y="Total number of students") + scale_x_discrete(labels = function(x) str_wrap(x, width = 10))
ggplotly(p2)
```

### Table 1.1: Total number of registered by year (as at 31 December 2021)

```{r}
df2 <- df2 %>% arrange(y2021)
colnames(df2) <- c("Faculty name", "2017", "2018", "2019", "2020", "2021")
knitr::kable(df2)
```


Column {data-width=300}
-----------------------------------------------------------------------



### Figure 1.2: New registrations by year (as at 31 December 2021) 


```{r, fig.height=10}
# Internal undergraduate enrolment (New registrations) as at 31st December (2017-2021)
y1516 <- c(837, 628, 1215, 151, 321, 121, 70)
y1617 <- c(877, 698, 1213, 160, 321, 120, 71)
y1718 <- c(942, 743, 1223, 161, 318, 121, 74)
y1819 <- c(939, 781, 1216, 160, 323, 120, 88)
y1920 <- c(984, 875, 1348, 193, 491, 186, 155)
df3 <- tibble(faculty_names, y1516, y1617, y1718, y1819, y1920)
colnames(df3) <- c("Faculty", "2015/2016", "2016/2017", "2017/2018", "2018/2019", "2019/2020")
df31 <- pivot_longer(df3, 2:6, "Year", "Value")
p2 <- ggplot(df31, aes(x=Faculty, y=value,  fill=Year)) + geom_bar(stat="identity", position="dodge") +  scale_fill_manual(values=rev(vec2g))+theme( axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) + labs(x="", y="New registrations") + scale_x_discrete(labels = function(x) str_wrap(x, width = 10))
ggplotly(p2)
```

### Table 1.2: New registrations by year (as at 31 December 2021)

```{r}
df3 <- df3 %>% arrange(y1920)
colnames(df3) <- c("Faculty name", "2015/2016", "2016/2017", "2017/2018", "2018/2019", "2019/2020")
knitr::kable(df3)  
```

# External undergraduate students and Postgraduate student registration

Column {data-width=300}
-----------------------------------------------------------------------


### Figure 2.1 External Undergraduate Student Registrations as at 31 December 2021

```{r}
Degree <- c("Bachelor of Arts (General) External Degree", "Bachelor of Humanities and Social Science             (General) External Degree", "Bachelor of Social Science (General) External Degree in Environmental and Development Studies", "Bachelor of Social Science (General) External Degree in Environmental and Development Studies", "B.Sc. Business Administration  (General) External Degree", "B.Sc. Management (Public) (General) External Degree", "B.Com (General) External Degree", "B.Sc. Business Studies (General) External Degee", "Total")
Count <- c(69536, 6550, 637, 2906, 8616, 9503, 12909, 422, 111079)
Percentage <- round((Count/111079)*100, 2)
df4 <- tibble(Degree, Count, Percentage)
p4 <- ggplot(df4[1:6,], aes(x=reorder(Degree, Count), y=Count)) +
  geom_bar(stat="identity", col="#800026", fill="#800026") + labs(y="Number of students", x="") + theme( axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) + scale_x_discrete(labels = function(x) str_wrap(x, width = 40))
p4
```


### Table 2.1 External Undergraduate Student Registrations as at 31 December 2021

```{r}
df4 <- df4 %>% arrange(Percentage)
colnames(df4) <- c("Degree", "Total number of students registered", "Percentage (%)")
kable(df4)
```

Column {data-width=300}
-----------------------------------------------------------------------



### Figure 2.1 Postgraduate Student Registrations as at 31 December 2021

```{r}
Degreepg <- factor(c("PG Certificate", "PG Diploma", "Master Degrees", "M.Phil Degree", "Doctoral Degree", "Total"), levels=c("PG Certificate", "PG Diploma", "Master Degrees", "M.Phil Degree", "Doctoral Degree", "Total"))

new <- c(15, 45, 402, 19, 58, 539)
Percentagenew <- round((new/539)*100, 2)
total <- c(57, 199, 2200, 197, 210, 2863)
Percentagetotal <- round((total/2863)*100, 2)
df4 <- tibble(Degreepg, new, Percentagenew, total, Percentagetotal)
ggplot(df4[1:5,], aes(x=Degreepg, y=new)) +
  geom_bar(stat="identity", col="#feb24c", fill="#feb24c") + labs(y="Number of students", x="") + theme( axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) + scale_x_discrete(labels = function(x) str_wrap(x, width = 50))
```


### Table 2.1 Postgraduate Student Registrations as at 31 December 2021

```{r}

colnames(df4) <- c("Degree", "Number of new registrations", "Percentage (%)" ,"Total number of students registered", "Percentage (%)")
kable(df4)
```

# Graduate output details

Column {data-width=400}
-----------------------------------------------------------------------

### Figure 3.1:  Graduate output details (Internal first degree) - 2021: Student counts

```{r}

first_class <- c(59, 49, 151, 7, 13, 8, 6)
second_upper <- c(452, 204, 273, 33, 107, 38, 19)
second_lower <- c(203, 123, 282, 53, 107, 38, 19)
pass <- c(121, 255, 479, 61, 84, 13, 33)
total_graduated <- c(835, 631, 1185, 154, 289, 103, 76)
df5 <- tibble(faculty_names, first_class, second_upper, second_lower, pass)
df5 <- df5 %>% arrange(pass)
df52 <- pivot_longer(df5, 2:5, "Type", "value")
df52$Type <- factor(df52$Type, levels = c("first_class", "second_upper", "second_lower", "pass"))
p7 <- ggplot(df52, aes(x=faculty_names, y=value,  fill=Type)) + geom_bar(stat="identity", position="dodge") +  scale_x_discrete(labels = function(x) str_wrap(x, width = 40)) + labs(x="", y="Number of students")
p8 <- ggplot(df52, aes(x=faculty_names, y=value,  fill=Type)) + geom_bar(stat="identity", position="fill") +scale_y_continuous(labels=scales::percent)  +  scale_fill_manual(values=rev(vec2g))+scale_x_discrete(labels = function(x) str_wrap(x, width = 40))+ labs(x="", y="Percentage of students")
ggplotly(p7)
```


### Figure 3.2:  Graduate output details (Internal first degree) - 2021: Cummulative percentage

```{r}
ggplotly(p8)
```

# Academic staff

Column {data-width=400}
-----------------------------------------------------------------------

### Figure 4.1:  Faculty-wise academic staff information (as at 31st December 2021)

```{r}
SP <- c(7, 11, 12, 11, NA, NA, NA)
P <- c(28, 31, 35, 29, 1, NA, 2)
AP <- c(4, NA, 2, 3, NA, NA, NA)
SL1 <- c(47, 27, 46, 22, 6, 3, 5)
SL2 <- c(27, 56, 51, 24, 45, 19, 17)
L <- c(8, 12, 18, 10, 5, 1, 2)
LP <- c(19, 17, 24, 16, 9, NA, 10)

df6 <- tibble(faculty_names, SP, P, AP, SL1, SL2, L, LP)
colnames(df6) <- c("Faculty", "Senior Professor", "Professor", "Associate Professor", "Senior Lecturer Gr. I", "Senior Lecturer Gr. II", "Lecturer", "Lecturer Probation")
df62 <- pivot_longer(df6, 2:8, "Category", "value")
df62$Category <- factor(df62$Category, levels = c("Senior Professor", "Professor", "Associate Professor", "Senior Lecturer Gr. I", "Senior Lecturer Gr. II", "Lecturer", "Lecturer Probation"))
col <- c("#1b9e77", "#d95f02", "#7570b3",
         "#e7298a", "#66a61e", "#e6ab02", "#a6761d")
extra <- c("#edf8b1", "#c7e9b4", "#7fcdbb", "#41b6c4", "#1d91c0", "#225ea8", "#0c2c84")
p9 <- ggplot(df62, aes(x=Faculty, y=value,  fill=Category)) + geom_bar(stat="identity", position="dodge") +  scale_fill_viridis_d() +  scale_x_discrete(labels = function(x) str_wrap(x, width = 40)) + labs(x="", y="Number of academics")
ggplotly(p9)
```

### Academic staff qualifications: 2018 - 2021

```{r}
Year <- 2018:2021
FD <- c(74, 87, 73, 72)
Masters <- c(147, 147, 149, 156)
MPhil <- c(42, 42, 43, 41)
MDMS <- c(61, 56, 63, 65)
PhD <- c(296, 309, 361, 400)
dfqual <- tibble(Year, FD, Masters, MPhil, MDMS, PhD)
colnames(dfqual) <- c("Year", "First Degree & PG Dip.", "Masters", "M.Phil", "MD/MS", "Doctoral Degrees")
dfqual2 <- pivot_longer(dfqual, 2:6, "Degree", "value")
dfqual2$Degree <- factor(dfqual2$Degree, levels = c("First Degree & PG Dip.", "Masters", "M.Phil", "MD/MS", "Doctoral Degrees"))

p10 <- ggplot(dfqual2, aes(x=Year, y=value,  fill=Degree)) + geom_bar(stat="identity", position="dodge") + scale_fill_manual(values = rev(vec4))  + labs( y="Number of academics")
ggplotly(p10)

```


# About Us

Visit: https://www.sjp.ac.lk/#

Contact: 

University of Sri Jayewardenepura,
Gangodawila,
Nugegoda,
Sri Lanka.




